Intentional release of native species undermines ecological stability

### 2022-10-22 rmd/supporting_info.Rmd
Update supporting_info.Rmd

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 10.5pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

suppressMessages(source(here::here("code/set_rmd.R")))
```

```{=tex}
\newpage
\pagestyle{fancy}
\fancyhead[L]{Terui et al.}
\fancyhead[C]{}
\setlength{\headheight}{13.7pt}
\pagenumbering{arabic}
\def\figurename{Figure S\hspace{-.4ex}}
\def\tablename{Table S\hspace{-.4ex}}
```
# Methods

@@

suppressMessages(source(here::here("code/table_param_set.R")))
knitr::kable(df_param,
             format = "markdown",
             caption = "Parameter values used in the whole community simulation.")

@@

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds. Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge. Body size is coded as follows: maximum total length (TL) $< 100$ mm (S), $100\\le$  TL $\\le 200$ (M), and TL $> 200$ (L).")
```

@@

knitr::kable(df_prior,
             align = rep("l", 3),
             format = "markdown",
             caption = "Prior distributions used in the Bayesian models. See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors. The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).")

@@

@@

knitr::kable(df_ssm_ar,
             align = c(rep("l", 2), rep("r", 2)),
             format = "markdown",
             caption = "Median estimates for key parameters of the state-space autoregressive model. Site-specific parameters were excluded due to a large number of parameters.")

@@

knitr::kable(df_ricker,
             align = c(rep("l", 2), rep("r", 2)),
             format = "markdown",
             caption = "Median estimates for key parameters of the state-space Ricker model. Site-specific parameters were excluded due to a large number of parameters.")

@@

  knit_chunk <- paste0("## Parameter estimates for the regression model (", c_text[i], ")",
                       "\n```{r tab-reg", i, "}
                       \n\n
                       kable(list_reg[[",i,"]],
                             align = c(rep('l', 2), rep('r', 4)),
                             format = 'markdown',
                             caption = table_legend[",i,"])
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")

>>>>

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 10.5pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \captionsetup{width=1.35\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

suppressMessages(source(here::here("code/set_rmd.R")))

```{=tex}
\newpage
\pagestyle{fancy}
\fancyhead[L]{Terui et al.}
\fancyhead[C]{}
\pagenumbering{arabic}
\def\figurename{Figure S\hspace{-.4ex}}
\def\tablename{Table S\hspace{-.4ex}}
```
# Methods

@@

suppressMessages(source(here::here("code/table_param_set.R")))
knitr::kable(df_param,
             escape = FALSE,
             booktabs = TRUE,
             caption = "Parameter values used in the whole community simulation.") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

knitr::kable(df_sp_list,
             booktabs = TRUE,
             escape = FALSE,
             caption = "Fish species found in the study watersheds. Body size is coded as follows: maximum total length (TL) $< 100$ mm (S), $100\\le$  TL $\\le 200$ (M), and TL $> 200$ (L).") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position",
                                              "scale_down"))
```

Note: Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975; @gotoLifeHistoryDistibution1981; @ministryofenvironmentofjapanThreatenedWildlifeJapan2014; @natsumedaEvaluationEcologicalFeatures2010; @fishbaseFishBaseHttpsWww] and expert knowledge.

@@

knitr::kable(df_prior,
             align = rep("l", 3),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Prior distributions used in the Bayesian models. The parameter $\\pmb{\\omicron}$ is a vector of prior scales ($\\pmb{\\omicron}=2.5,...,2.5$).") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

See Durante [@duranteNoteMultiplicativeGamma2017] for multiplicative gamma priors.

@@

knitr::kable(df_ssm_ar,
             align = c(rep("l", 2), rep("r", 2)),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Median estimates for key parameters of the state-space autoregressive model. Site-specific parameters were excluded due to a large number of parameters.") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

knitr::kable(df_ricker,
             align = c(rep("l", 2), rep("r", 2)),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Median estimates for key parameters of the state-space Ricker model. Site-specific parameters were excluded due to a large number of parameters.") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

  knit_chunk <- paste0("## Parameter estimates for the regression model (", c_text[i], ")",
                       "\n```{r tab-reg", i, "}
                       \n\n
                       kable(list_reg[[",i,"]],
                             align = c(rep('l', 2), rep('r', 4)),
                             escape = FALSE,
                             booktabs = TRUE,
                             caption = table_legend[",i,"]) %>% 
  kableExtra::kable_styling(latex_options = 'HOLD_position')

                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")
